Oral Manuscript

### 2018-06-06 index.Rmd
bug fix
adjusted travis, fixed bug in report

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [lib.bib, packages.bib]
biblio-style: apalike
colorlinks: yes
lot: yes
lof: yes
fontsize: 12pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

@@

Blah...

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

>>>>

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
#bibliography: [lib.bib, packages.bib]
bibliography: lib.bib
biblio-style: apalike
colorlinks: yes
lot: yes
lof: yes
fontsize: 12pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE)

# ```{r include=FALSE}
# # automatically create a bib database for R packages
# knitr::write_bib(c(
#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
# ), 'packages.bib')
# ```

```

@@
